D3064R0: How to Avoid OOTA Without Really Trying

### 2024-03-05 ootavacuous.tex
Three-Process OOTA: Wordsmith.
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

Listing~\ref{lst:Three-Process Version of JMM Causality Test Case 4}
shows a different way of expanding
Listing~\ref{lst:Causality Test Case 4}
(discussed in
Appendix~\ref{app:Causality Test Case 4})
from two threads to three threads.
The \co{herd7} tool finds OOTA values, as expected.

>>>>

Listing~\ref{lst:Three-Process Version of JMM Causality Test Case 4}
expands
Listing~\ref{lst:Causality Test Case 4}
(discussed in
Appendix~\ref{app:Causality Test Case 4})
from two threads to three threads.
The \co{herd7} tool finds OOTA values, as expected.
